IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-11-17 main.tex
:triangular_flag_on_post: TCOM 211117

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
			\label{fi:system}
		\end{figure}

@@

		\begin{subsection}{Receiving Modes}
			\begin{figure}[!t]
				\centering
				\subfloat[TS receiver\label{fi:ts_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\centering
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
								to[short,-o] ++(0,-1) node[below]{Time Switcher}
								to[short] node[spdt,anchor=in](s){} ++(0.5,0);

							\draw (s.out 1) node[above right]{$1-\eta$}
								to ++(1.25,0)
								to ++(0,0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);

							\draw (s.out 2) node[below right]{$\eta$}
								to ++(1.25,0)
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\\
				\subfloat[PS receiver\label{fi:ps_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
								to[short,-o] ++(0,-1)
								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
							\draw (c.right up)
								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
								to ++(0,0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
							\draw (c.right down)
								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\caption{Diagrams of practical co-located receivers.}
				\label{fi:receiver}
			\end{figure}

@@

		\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
			\begin{figure}[!t]
				\centering
				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
					\resizebox{0.45\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
					\resizebox{0.45\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
				\caption{Equivalent circuits of receive antenna and energy harvester.}
			\end{figure}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/channel_amplitude.tex}
			}
			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
			\label{fi:channel_amplitude}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_noise.tex}
				}
			}
			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/splitting_ratio_noise.tex}
				}
			}
			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss product\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_1mhz.tex}
				}
			}
			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_10mhz.tex}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$. $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
		\end{figure}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{system.eps_tex}
			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
			\label{fi:system}
		\end{figure}

@@

		\begin{subsection}{Receiving Modes}
			\begin{figure}[!t]
				\centering
				\subfloat[TS receiver\label{fi:ts_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\includegraphics{assets/ts_receiver.eps}
					}
				}
				\\
				\subfloat[PS receiver\label{fi:ps_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\includegraphics{assets/ps_receiver.eps}
					}
				}
				\caption{Diagrams of practical co-located receivers.}
				\label{fi:receiver}
			\end{figure}

@@

		\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
			\begin{figure}[!t]
				\centering
				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
					\resizebox{0.45\columnwidth}{!}{
						\includegraphics{assets/antenna_equivalent_circuit.eps}
					}
				}
				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
					\resizebox{0.45\columnwidth}{!}{
						\includegraphics{assets/a_single_diode_rectifier.eps}
					}
				}
				\caption{Equivalent circuits of receive antenna and energy harvester.}
			\end{figure}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.eps_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\includegraphics{assets/channel_amplitude.eps}
			}
			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
			\label{fi:channel_amplitude}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_subband.eps}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/waveform_subband.eps}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_noise.eps}
				}
			}
			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/splitting_ratio_noise.eps}
				}
			}
			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_distance.eps}
				}
			}
			\subfloat[Path loss product\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/path_loss.eps}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_tx.eps}
				}
			}
			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/scaling_tx.eps}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.425\columnwidth}{!}{
					\includegraphics{assets/re_reflector.eps}
				}
			}
			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
				\resizebox{0.475\columnwidth}{!}{
					\includegraphics{assets/scaling_reflector.eps}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_irs_1mhz.eps}
				}
			}
			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_irs_10mhz.eps}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_csi.eps}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\includegraphics{assets/re_quantization.eps}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$. $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
		\end{figure}
